High Resolution Identification of Protein-DNA Binding Events and Quality Control for ChIP-exo data

### 2015-11-12 rmarkdown/chip_exo_paper.Rnw
added comments in the enrichment plot

While the number of produced ChIP-exo data keeps increasing,
characteristicos of ChIP-exo data and optimal strategies for
experimental design and analysis of ChIP-exo data are not fully
investigated yet, including issues of sequence biases inherent to
ChIP-exo data, choice of optimal statistical methods, and
determination of optimal sequencing deoth. However, currently, the
number of available ChIP-exo data is still limited and their
sequencing depths are still insufficient for such investigation. To
address this limitation we gathered ChIP-exo data from diverse
organisms: CTCF factor in human \cite{exo1}; ER factor in human and
FoxA1 factor in mouse from \cite{exoillumina}; and generated
$\sigma^{70}$ factor in Escherichia coli (E. Coli) under aerobic ($ +
O_2$) condition, and treated by rifampicin by 0 and 20 minutes.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = .8\textwidth]{../figs/for_paper/Sig70_enrichment.pdf}
  \includegraphics[width = .8\textwidth,page =3]{../figs/for_paper/Local_SCC_indicator_by_strata.pdf}
  \caption{Enrichment and else}
  \label{fig:enrich}
\end{figure}

% \begin{figure}[h]
%   \centering

%   \caption{This is a place-holder figure by now. The idea of this segments it }
%   \label{fig:fsr}
% \end{figure}

@@

\section*{Supplement figures}

\subsection*{Strand cross-correlation for ChIP-exo data}

>>>>

While the number of produced ChIP-exo data keeps increasing,
characteristics of ChIP-exo data and optimal strategies for
experimental design and analysis of ChIP-exo data are not fully
investigated yet, including issues of sequence biases inherent to
ChIP-exo data, choice of optimal statistical methods, and
determination of optimal sequencing deoth. However, currently, the
number of available ChIP-exo data is still limited and their
sequencing depths are still insufficient for such investigation. To
address this limitation we gathered ChIP-exo data from diverse
organisms: CTCF factor in human \cite{exo1}; ER factor in human and
FoxA1 factor in mouse from \cite{exoillumina}; and generated
$\sigma^{70}$ factor in Escherichia coli (E. Coli) under aerobic ($ +
O_2$) condition, and treated by rifampicin by 0 and 20 minutes.

@@

In ChIP-exo experiments and input samples is often unavailable,
therefore to determine the quality of a ChIP-exo experiment is
necesary to address the balance between the enrichment and the library
complexity of the experiment. To diagnose this balance we considered
the Average Read Coverage (ARC) and the Unique Read Coverage Rate (URCR) which are defined as:

\begin{align}
  \mbox{ARC} &= \frac{\text{Nr. of reads in the region}}{\text{Width of the region}} \nonumber \\
  \mbox{URCR} &= \frac{\text{Nr. of reads mapped to only one position
      in the region}}{\text{Nr. of reads in the region}} \nonumber
\end{align}

\begin{figure}[h!]
  \centering
  \includegraphics[width = .8\textwidth]{../figs/for_paper/Sig70_enrichment.pdf}
  \includegraphics[width = .8\textwidth,page =3]{../figs/for_paper/Local_SCC_indicator_by_strata.pdf}
  \caption{A) For all $\sigma^{70}$ ChIP-exo experiments we are
    comparing the ARC against the URCR.}
  \label{fig:enrich}
\end{figure}

@@

% \newpage
% \section*{Supplement figures}
% \subsection*{Strand cross-correlation for ChIP-exo data}
